Reversed motion direction illusion: influence of (spatially congruent) subsequent own-body motion on self-motion perception

### 2017-07-19 manuscript.Rmd
first version of introduction done

The structure of the three experiments with the discrimination tasks is ideal to study the perceptual decision making process. As far as we know, the decision making process has never been investigated more closely in vestibular motion aftereffects. However, a joint analysis of response and response time would provide more detailed information about the dynamics of the underlying process. A commonly used model for a joint analysis is the Drift Diffusion Model (DDM) [@ratcliff_diffusion_2008]. In the DDM it is assumed that the decision making process relies on the acculumation of noisy sensory evidence over time. A response is given when a threshold for one of the two possibilities is reached. Several parameters describe the decision making process: The drift rate stands for the speed of evidence accumulation for one of the two response options, the boundary separation parameter serves as the threshold for the needed evidence to make response, the non deicision time parameter covers the portion within a response not involved in the deicision making process (e.g. motor execution) and the starting point indicates a point within the boundary from which evidence accumulation starts. Other studies within the field of perceptual decision making [@ellis_vestibular_2017; @wiech_influence_2014] used DDM to disentagle influence of prior information on parameters of the decision making process. From another point of view, in the MAE a first movement introduces prior information which influences the evaluation of the second motion. A DDM allows us to investigate altered sensory processing and a perceptual decision-making bias separately. So far MAE or TAE did not consider those two different biases.

>>>>

The structure of the three experiments with the discrimination tasks is ideal to study the perceptual decision making process. As far as we know, the decision making process has never been investigated more closely in vestibular motion aftereffects. However, a joint analysis of response and response time would provide more detailed information about the dynamics of the underlying process. A commonly used model for a joint analysis is the Drift Diffusion Model (DDM) [@ratcliff_diffusion_2008]. In the DDM it is assumed that the decision making process relies on the acculumation of noisy sensory evidence over time. A response is given when a threshold for one of the two possibilities is reached. Several parameters describe the decision making process: The drift rate stands for the speed of evidence accumulation for one of the two response options, the boundary separation parameter serves as the threshold for the needed evidence to make response, the non deicision time parameter covers the portion within a response not involved in the deicision making process (e.g. motor execution) and the starting point indicates a point within the boundary from which evidence accumulation starts. Other studies within the field of perceptual decision making [@ellis_vestibular_2017; @wiech_influence_2014] used DDM to disentagle influence of prior information on different parameters of the decision making process. Applied to MAEs, it appears that a first motion stimulation (in our case vestibular) influences the judgment of the subsequent motion discrimantion task by introducing a bias. However, it remians to be seen whether such a bias for the opposite direction shifts the starting point to the opposite direction, which would mean that a first motion alters the perceptual decision making, or whether the first motion affects the drift rate and thus changes the acculumation processes, which would be indicative for altered sensory processing [@wiech_influence_2014].
